Investigating Neolithic pottery usage in the Yanyuan Basin in Southwest China using organic residue analysis

### 2023-01-21 analysis/paper/paper.Rmd
corrected a reference

<!--Info about Guijiabao-->
Among those archaeological sites in Yanyuan, Guijiabao located in the southwestern part of the basin is a unique site with relatively complete and continuous occupation from the early Neolithic period to the historical period [@Guijiabao2017a; @Guijiabao2017b]. Survey in 2015 and subsequent excavations from 2016 to 2019 reveal abundant archaeological materials and features, such as semi-subterranean houses, ground houses, post holes, ash pits, ditches, and burials, suggesting that Guidiabao is a settlement site with long-term occupation [@Hao2022]. The chronology of Guijiabao can be divided into three temporal phases based on 19 radiocarbon dates from plant remains and a human bone, including the Neolithic period (5000-3700 BP), the Bronze Age (3200-2700 BP.), and the late North Song to early Ming Dynasties (1200-500 BP) [@Hao2022]. For the Neolithic period, it can be further separated into two subphases, 5000-4500 cal. BP and 4500-3700 cal. BP, according to the content of artifact assemblages and ceramic forms and styles. The archaeobotanical remains found at Guidiabao reveal the evidence of crop cultivation dominated by foxtail and broomcorn millet that can be traced back to 5000 BC and mixed cultivation of millet and rice in a later period (3000–1700 BC) [@Guijiabao2014; @Hao2022].

<!--Info about Gaoshan-->
Gaoshan site is located in the southwestern part of the Chengdu Plain. Excavations at Gaoshan unearthed house foundations, burials, ashpits with abundant materials that could represent the earliest phases of the Baodun culture [citations].

>>>>

<!--Info about Guijiabao-->
Among those archaeological sites in Yanyuan, Guijiabao located in the southwestern part of the basin is a unique site with relatively complete and continuous occupation from the early Neolithic period to the historical period [@Guijiabao2017a; @Guijiabao2017b]. Survey in 2015 and subsequent excavations from 2016 to 2019 reveal abundant archaeological materials and features, such as semi-subterranean houses, ground houses, post holes, ash pits, ditches, and burials, suggesting that Guidiabao is a settlement site with long-term occupation [@Hao2022]. The chronology of Guijiabao can be divided into three temporal phases based on 19 radiocarbon dates from plant remains and a human bone, including the Neolithic period (ca. 5000-3700 BP), the Bronze Age (ca. 3200-2700 BP), and the late North Song to early Ming Dynasties (ca. 1200-500 BP) [@Hao2022]. For the Neolithic period, it can be further separated into two subphases, 5000-4500 ca. BP and 4500-3700 ca. BP, according to the content of artifact assemblages and ceramic forms and styles.

Among those various ceramic styles, the decorations such as incised geometric patterns and impressed dot patterns are the common styles that have also been found in western Yunnan area, indicative of frequent interactions between Guijiabao and sites in Yunnan [@Guijiabao2017a]. The archaeobotanical remains at Guijiabao reveal the evidence of crop cultivation dominated by foxtail and broomcorn millet that can be traced back to 5000 BC with no finding of rice grains based on the flotation results in 2015 [@Guijiabao2016].

<!--Info about Gaoshan-->
The site of Gaoshan is located in the southwestern margin of the Chengdu Plain, an alluvial plain between the Sichuan Basin and the Tibetan Plateau (Figure \@ref(fig:SW-china-map)). Excavations at Gaoshan revealed abundant pottery, stone artifacts, and features such as house foundations, burials, and middens. According to the pottery forms and decorations, Gaoshan can be categorized into the earliest phase of the Baodun period, the earlies Neolithic culture (ca. 4500-4000 BP)in Chengdu Plain [citations].
